### 2020-08-20 ReadMe.rmd
fix typo
updates readme

```{}
docker push vlucet/land_con_monteregie:3.6.2-1
```

@@

  - Run docker image (`docker run [options] vlucet/land_con_monteregie:3.6.2-1 /bin/bash && cd ~/land_con_monteregie`), executing a command that starts bash and move to the repo directory (`/bin/bash && cd ~/land_con_monteregie`), with options to run an interactive terminal (`-it`) with the rstudio user (needed, `-u rstudio`) with authentification disabled (` DISABLE_AUTH=true`).

>>>>

```{}
docker pull vlucet/land_con_monteregie:3.6.2-1
```

@@

  - Run docker image (`docker run [options] vlucet/land_con_monteregie:3.6.2-1 /bin/bash && cd ~/land_con_monteregie`), executing a command that starts bash and move to the repo directory (`/bin/bash && cd ~/land_con_monteregie`), with options to run an interactive terminal (`-it`) with authentification disabled (` DISABLE_AUTH=true`).
